A Theory of Bidirectional Type Synthesis for Simple Types

### 2023-07-11 tex/sec1-intro.tex
[ tex ] Minor changes

This paper is structured as follows.
We first present a concrete overview of our theory using simply typed $\lambda$-calculus in \cref{sec:key-ideas}, prior to developing a general framework for specifying bidirectional type systems in \cref{sec:defs}.
Following this, we discuss mode decoration and related properties in \cref{sec:pre-synthesis}.
The most heavyweight technical contribution lies in \cref{sec:type-synthesis}, where we introduce mode-correctness and bidirectional type synthesis.
Some examples other than simply typed $\lambda$-calculus are given in \Cref{sec:example}.
We sketch the design of the \Agda formalisation of our theory in \cref{sec:formalisation} briefly.
We conclude in \cref{sec:future}, where we reflect on related techniques that can be used to improve the formal development and potential challenges in extending our theory to a more general setting.

>>>>

This paper is structured as follows.
We first present a concrete overview of our theory using simply typed $\lambda$-calculus in \cref{sec:key-ideas}, prior to developing a general framework for specifying bidirectional type systems in \cref{sec:defs}.
Following this, we discuss mode decoration and related properties in \cref{sec:pre-synthesis}.
The most heavyweight technical contribution lies in \cref{sec:type-synthesis}, where we introduce mode-correctness and bidirectional type synthesis.
Some examples other than simply typed $\lambda$-calculus are given in \Cref{sec:example}.
We sketch the design of our formalisation in \cref{sec:formalisation} briefly.
We conclude in \cref{sec:future}, where we reflect on techniques that may improve the formal development and potential challenges in extending our theory to a more general setting.
